---
title: "Gen's NA"
author: "DZ"
date: '2022-07-31'
output: word_document
---

```{r include=FALSE}
library(bootnet)
library(haven)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)
library(tidyverse)
library(naniar)
library(mice)

GData <- read_sav("C:/Users/danie/Desktop/Honours Super/Genevieve/dataset.sav")
```


## Percentage of missing data in the dataset and if missing data is missing completely at random (MCAR)
```{r echo=FALSE, warning=FALSE, message=FALSE}
GD1 <- GData%>%
  select(7,102:107,176:186,49:57,187:195,291:296,344:354,238:246,377:385)

## This calculates % of missing data
Gtotalcells <- prod(dim(GD1))
Gmissingcells <- sum(is.na(GD1))
(Gmissingcells * 100)/(Gtotalcells)

mcar_test(GD1)
```

## Variables with highest number of missing values
```{r echo=FALSE, warning=FALSE, message=FALSE}
GD1 %>%
  select(!1) %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(cols = everything(), names_to = "names", values_to = "values") %>%
  arrange(desc(values)) %>%
  mutate(perc=(values)/462) %>%
  slice_head(n = 20)
```
```{r include=FALSE}

## Data imputation with Predictive Mean Matching (PMM) and 50 iterations 
GD2 <- sapply(GD1, haven::zap_labels) ## this line converts doubles into integers
#Gimputed_data <- mice(GD2, m=5, maxit = 50, method = 'pmm', seed = 500)
#summary(Gimputed_data)
#GcompleteData <- as_tibble(complete(Gimputed_data,2))
setwd("C:/Users/danie/Desktop/Honours Super/Genevieve")
#write_sav(GcompleteData, "Complete_data_g.sav")
GD3 <- read_sav("Complete_data_g.sav")

GD4 <- GD3 %>%
  select(!Gender)
```
## Estimate network
```{r echo=FALSE, warning=FALSE, message=FALSE}
Gnetwork1 <- estimateNetwork(GD4, default="EBICglasso")
Gnetwork1

## these lines will write an excel file with your correlation matrix
Gcor_mat <-as_tibble(getWmat(Gnetwork1))
#write_csv(Gcor_mat, "Correlation matrix_Gen.csv")
```
```{r include=FALSE}
Gb1 <- bootnet(Gnetwork1, boots=1000, type="nonparametric", nCores = 8,
              statistics=c("strength", "expectedInfluence", "edge"))
Gb2 <- bootnet(Gnetwork1, boots=1000, type="case", nCores = 8,
              statistics = c('strength','expectedInfluence',
                             'betweenness','closeness'))
```

## Correlation stability coefficient and plot
CS larger than 0.7 is excellent, 0.5 < CS < 0.7 is acceptable, CS < 0.5 not acceptable
```{r echo=FALSE, warning=FALSE, message=FALSE}
corStability(Gb2)
Gen_plot_cs <- plot(Gb2, "all")
Gen_plot_cs

#ggsave("Figure_1.tiff", Gen_plot_cs, width = 6, height = 6, dpi=300)
```

## Network accuracy
We plot Bootstrapped edge CI's - here we focus on large discrepancies between the red (observed values) and black (bootstrapped mean) lines. We can also look at the size of CI's with larger grey areas showing less confidence
```{r echo=FALSE, warning=FALSE, message=FALSE}
Gen_plot_boot <- plot(Gb1, labels = F, order = "sample")
Gen_plot_boot
#ggsave("Figure_2.tiff", Gen_plot_boot, width = 6, height = 6, dpi=300)
```
```{r include=FALSE}
## Group nodes per disorder
Ggroups1 <- list("BSMAS Wave 1" = c(1:6),"OGD Wave 1"=c(7:17),
                "IGD Wave 1"=c(18:26),"IDS Wave 1"=c(27:35),
                "BSMAS Wave 2" = c(36:41),"OGD Wave 2"=c(42:52),
                "IGD Wave 2"=c(53:61),"IDS Wave 2"=c(62:70)) 

qgraph(Gcor_mat, groups=Ggroups1,
                           color=c('lightblue','orange','coral1','limegreen',
                             'skyblue2','orange4','coral4','palegreen4'),
       layout = "spring", minimum = 0, cut = 0, curveAll = T, curveDefault = 0.5,
       label.color="black", label.prop = 1, label.scale = T, label.scale.equal = T,
       legend.cex = 0.4, font = 2, vsize = 4, posCol = "blue",
       borders = T, border.color = 'black', border.width = 0.2,
       vTrans = 220, usePCH = F, node.resolution = 150)
```

```{r include=FALSE}
#Gen_plot_Network <- qgraph(Gcor_mat, groups=Ggroups1,
 #                          color=c('lightblue','orange','coral1','limegreen',
  #                           'skyblue2','orange4','coral4','palegreen4'),
   #    layout = "spring", minimum = 0, cut = 0, curveAll = T, curveDefault = 0.5,
    #   label.color="black", label.prop = 1, label.scale = T, label.scale.equal = T,
     #  legend.cex = 0.4, font = 2, vsize = 4, posCol = "blue",
      # borders = T, border.color = 'black', border.width = 0.2,
       #vTrans = 220, usePCH = F, node.resolution = 150, filetype = 'tiff',filename="figure_3")
```

## Plot centrality indices and centrality table
```{r echo=FALSE, warning=FALSE, message=FALSE}

Gen_plot_cent <- centralityPlot(Gnetwork1, include = "all", 
               scale = "z-scores", orderBy = "ExpectedInfluence")+
  theme(aspect.ratio = 6/1)
#ggsave("Figure_4.tiff", Gen_plot_cent, width = 8, height = 10, dpi=300)
Gen_plot_cent

Gen_plot_cent$data$measure <- recode_factor(Gen_plot_cent$data$measure, 
                                            Betweenness = "Between", ExpectedInfluence = "Exp inf",
                                            Closeness = "Closeness")


GCent_table <- as_tibble(centralityTable(Gnetwork1))
GCent_table %>%
  pivot_wider(names_from = measure, values_from = value)%>%
  select(node,ExpectedInfluence) %>%
  arrange(desc(ExpectedInfluence))%>%
  slice_head(n=10)

GCent_table %>%
  pivot_wider(names_from = measure, values_from = value)%>%
  select(node,Strength) %>%
  arrange(desc(Strength))%>%
  slice_head(n=10)

GCent_table %>%
  pivot_wider(names_from = measure, values_from = value) %>%
  select(node,Betweenness) %>%
  arrange(desc(Betweenness))%>%
  slice_head(n=10)

GCent_table %>%
  pivot_wider(names_from = measure, values_from = value)%>%
  select(node,Closeness) %>%
  arrange(desc(Closeness))%>%
  slice_head(n=10)
```

## Plot bridge symptoms
```{r echo=FALSE, warning=FALSE, message=FALSE}
Ggraph1 <- qgraph::EBICglasso(cor(GD4), n=dim(GD4)[1])
Gb <- bridge(Ggraph1, communities = Ggroups1)
GBStrength <- Gb$`Bridge Strength`
GBBetween <- Gb$`Bridge Betweenness`
GBClose <- Gb$`Bridge Closeness`
GBExpect <- Gb$`Bridge Expected Influence (1-step)`
Gsymptoms <- GD4%>%
  pivot_longer(cols = c(1:70), names_to = "symptoms", values_to = "n")%>%
  select(symptoms) %>%
  slice_head(n=70)

GBsymptoms <- as_tibble(Gsymptoms,GBStrength,GBBetween,GBClose,GBExpect)%>%
  mutate(`Strength` = (GBStrength - mean(GBStrength))/sd(GBStrength))%>%
  mutate(`Between` = (GBBetween - mean(GBBetween))/sd(GBBetween))%>%
  mutate(`Closeness` = (GBClose - mean(GBClose))/sd(GBClose))%>%
  mutate(`Exp inf` = (GBExpect - mean(GBExpect))/sd(GBExpect))%>%
  pivot_longer(cols = c(2:5), names_to = "Bcent", values_to = "n") %>%
  ggplot(aes(n,symptoms)) +
  geom_point(size=1.5)+
  geom_line(group=1) +
  facet_wrap(vars(Bcent), nrow = 1) +
  labs(x = "", y = "") +
  theme(aspect.ratio = 6/1)
GBsymptoms

library(patchwork)
patch <- Gen_plot_cent + GBsymptoms


as_tibble(Gsymptoms,GBStrength,GBBetween,GBClose,GBExpect)%>%
  mutate(`Strength` = (GBStrength - mean(GBStrength))/sd(GBStrength))%>%
  mutate(`Between` = (GBBetween - mean(GBBetween))/sd(GBBetween))%>%
  mutate(`Closeness` = (GBClose - mean(GBClose))/sd(GBClose))%>%
  mutate(`Exp inf` = (GBExpect - mean(GBExpect))/sd(GBExpect))%>%
  arrange(desc(`Exp inf`))

#ggsave("Figure_10.tiff", patch, width = 14, height = 26, dpi=300)
```

## Examining effects of time point 1 on time point 2
```{r echo=FALSE, warning=FALSE, message=FALSE}
Longg <- Gcor_mat %>%
  slice(1:35) %>%
  select(36:70)
#write_csv(Longg,"Long cor mat.csv")

Longg$symptoms <- Gsymptoms%>% slice_head(n=35)
Longg%>%
  relocate(symptoms)%>%
  rowwise()%>%
  mutate(degree=rowSums(across(everything(), ~(.>0))))%>%
  mutate(expinf=sum(across(2:36))) %>%
  arrange(desc(expinf))%>%
  select(symptoms,degree,expinf) %>%
  head(n = 10)
```

# Gender analysis
```{r echo=FALSE, warning=FALSE, message=FALSE}
# Create dataset with only males
GMales <- GD3 %>%
  filter(Gender==1)%>%
  select(11:80)

## Create dataset with only females
GFemales <- GD3 %>%
  filter(Gender==0) %>%
  select(11:80)
```

## Estimate and plot male network
```{r echo=FALSE, warning=FALSE, message=FALSE}
Gcor_mat_men <-as_tibble(getWmat(Gnetwork_males <- estimateNetwork(GMales, default="EBICglasso")))
Gnetwork_males
Gen_plot_Network_males <- qgraph(Gcor_mat_men, groups=Ggroups1, color=c('lightblue','orange','coral1','limegreen',
                             'skyblue2','orange4','coral4','palegreen4'),
       layout = "spring", minimum = 0, cut = 0, curveAll = T, curveDefault = 0.5,
       label.color="black", label.prop = 1, label.scale = T, label.scale.equal = T,
       legend.cex = 0.4, font = 2, vsize = 4, posCol = "blue",
       borders = T, border.color = 'black', border.width = 0.2,
       vTrans = 220, usePCH = F, node.resolution = 150, filetype = 'tiff',filename="figure_6")

```

## Estimate and plot female network
```{r echo=FALSE, warning=FALSE, message=FALSE}
Gcor_mat_women <-as_tibble(getWmat(Gnetwork_females <- estimateNetwork(GFemales, default="EBICglasso")))
Gnetwork_females
Gen_plot_Network_females <- qgraph(Gcor_mat_women, groups=Ggroups1, color=c('lightblue','orange','coral1','limegreen',
                             'skyblue2','orange4','coral4','palegreen4'),
       layout = "spring", minimum = 0, cut = 0, curveAll = T, curveDefault = 0.5,
       label.color="black", label.prop = 1, label.scale = T, label.scale.equal = T,
       legend.cex = 0.4, font = 2, vsize = 4, posCol = "blue",
       borders = T, border.color = 'black', border.width = 0.2,
       vTrans = 220, usePCH = F, node.resolution = 150, filetype = 'tiff',filename="figure_7")

```

```{r include=FALSE}
GComparison <- NCT(Gnetwork_males, Gnetwork_females, gamma, it=100, binary.data = FALSE, 
                  paired = FALSE, weighted=TRUE, AND=TRUE, test.edges = FALSE, edges = 'ALL')
```

## Assess invariance across networks
```{r echo=FALSE, warning=FALSE, message=FALSE}

## Summary of statistics, sig results = non-invariance
summary(GComparison)

## Plotting differences
plot(GComparison, what="network")
plot(GComparison, what="strength")
```

## Plot centrality indices for males and females
```{r echo=FALSE, warning=FALSE, message=FALSE}
Gcent_males <- as_tibble(centralityTable(Gnetwork_males))
## Females
Gcent_females <- as_tibble(centralityTable(Gnetwork_females))

## Plot centrality indices for males and females
Gcent_males$Gender <- 'Males'
Gcent_females$Gender <- 'Females'
many_GDF <- list(Gcent_females,Gcent_males)
GGender <- as_tibble(Reduce(function(...) merge(..., all=T), many_GDF))

Gen_Genderplot <- GGender %>%
  ggplot(aes(x = node,  y = value, color = Gender, group = Gender)) +
  geom_point() +
  geom_line(size=1.0) +
  coord_flip() +
  facet_wrap(~measure, nrow = 1)+
  labs(x = "", y = "")+
  theme(aspect.ratio = 6/1)
Gen_Genderplot
ggsave("Figure_8.tiff", Gen_Genderplot, width = 8, height = 10, dpi=300)

table_cent <- GGender %>%
  pivot_wider(names_from = measure, values_from = value) %>%
  group_by(Gender)

table_cent %>%
  select(Gender,node,Closeness) %>%
  arrange(desc(Closeness))%>%
  slice_head(n=10)

table_cent %>%
  select(Gender,node,Betweenness) %>%
  arrange(desc(Betweenness))%>%
  slice_head(n=10)

table_cent %>%
  select(Gender,node,ExpectedInfluence) %>%
  arrange(desc(ExpectedInfluence))%>%
  slice_head(n=10)
 
table_cent %>%
  select(Gender,node,Strength) %>%
  arrange(desc(Strength))%>%
  slice_head(n=10) 

## Write excel files with correlation matrices for males and females
Gcor_mat_males <- as_tibble(getWmat(Gnetwork_males))
write_csv(Gcor_mat_males, "Correlation matrix males.csv")
Gcor_mat_females <- as_tibble(getWmat(Gnetwork_females))
write_csv(Gcor_mat_females, "Correlation matrix females.csv")
```

## Bridge symptoms for males and females
```{r echo=FALSE, message=FALSE, warning=FALSE}

## Prepping male data frame
Ggraph_males <- qgraph::EBICglasso(cor(GMales), n=dim(GMales)[1])
GBb_males <- bridge(Ggraph_males, communities = Ggroups1)
GBStrength_m <- GBb_males$`Bridge Strength`
GBBetween_m <- GBb_males$`Bridge Betweenness`
GBClose_m <- GBb_males$`Bridge Closeness`
GBExpect_m <- GBb_males$`Bridge Expected Influence (1-step)`
Gsymptoms_m <- GMales%>%
  pivot_longer(cols = c(1:70), names_to = "symptoms", values_to = "n")%>%
  select(symptoms) %>%
  slice_head(n=70)

GBsymptoms_m <- as_tibble(Gsymptoms_m,GBStrength_m,GBBetween_m,GBClose_m,SBExpect_m)%>%
  mutate(`Bridge strength` = (GBStrength_m - mean(GBStrength_m))/sd(GBStrength_m))%>%
  mutate(`Bridge between` = (GBBetween_m - mean(GBBetween_m))/sd(GBBetween_m))%>%
  mutate(`Bridge closeness` = (GBClose_m - mean(GBClose_m))/sd(GBClose_m))%>%
  mutate(`Bridge expect inf` = (GBExpect_m - mean(GBExpect_m))/sd(GBExpect_m))%>%
  pivot_longer(cols = c(2:5), names_to = "Bcent", values_to = "n")

## Prepping female data frame
Ggraph_females <- qgraph::EBICglasso(cor(GFemales), n=dim(GFemales)[1])
GBb_females <- bridge(Ggraph_females, communities = Ggroups1)
GBStrength_f <- GBb_females$`Bridge Strength`
GBBetween_f <- GBb_females$`Bridge Betweenness`
GBClose_f <- GBb_females$`Bridge Closeness`
GBExpect_f <- GBb_females$`Bridge Expected Influence (1-step)`
Gsymptoms_f <- GFemales%>%
  pivot_longer(cols = c(1:70), names_to = "symptoms", values_to = "n")%>%
  select(symptoms) %>%
  slice_head(n=70)

GBsymptoms_f <- as_tibble(Gsymptoms_f,GBStrength_f,GBBetween_f,GBClose_f,GBExpect_f)%>%
  mutate(`Bridge strength` = (GBStrength_f - mean(GBStrength_f))/sd(GBStrength_f))%>%
  mutate(`Bridge between` = (GBBetween_f - mean(GBBetween_f))/sd(GBBetween_f))%>%
  mutate(`Bridge closeness` = (GBClose_f - mean(GBClose_f))/sd(GBClose_f))%>%
  mutate(`Bridge expect inf` = (GBExpect_f - mean(GBExpect_f))/sd(GBExpect_f))%>%
  pivot_longer(cols = c(2:5), names_to = "Bcent", values_to = "n")

## Plot centrality indices for males and females
GBsymptoms_m$Gender <- 'Males'
GBsymptoms_f$Gender <- 'Females'
Gen_many_SDF_bridge <- list(GBsymptoms_m,GBsymptoms_f)
G_bridge_Gender <- as_tibble(Reduce(function(...) merge(..., all=T), Gen_many_SDF_bridge))

Gen_gender_bridgeplot <- G_bridge_Gender %>%
  ggplot(aes(x = symptoms,  y = n, color = Gender, group = Gender)) +
  geom_point() +
  geom_line(size=1.0) +
  coord_flip() +
  facet_wrap(~Bcent, nrow = 1)+
  labs(x = "", y = "")+
  theme(aspect.ratio = 6/1)
Gen_gender_bridgeplot

ggsave("Figure_9.tiff", Gen_gender_bridgeplot, width = 8, height = 10, dpi=300)

table_bridge_cent <- G_bridge_Gender %>%
  pivot_wider(names_from = Bcent, values_from = n) %>%
  group_by(Gender)

table_bridge_cent %>%
  select(Gender,symptoms,`Bridge closeness`) %>%
  arrange(desc(`Bridge closeness`))%>%
  slice_head(n=10)

table_bridge_cent %>%
  select(Gender,symptoms,`Bridge between`) %>%
  arrange(desc(`Bridge between`))%>%
  slice_head(n=10)

table_bridge_cent %>%
  select(Gender,symptoms,`Bridge expect inf`) %>%
  arrange(desc(`Bridge expect inf`))%>%
  slice_head(n=10)
 
table_bridge_cent %>%
  select(Gender,symptoms,`Bridge strength`) %>%
  arrange(desc(`Bridge strength`))%>%
  slice_head(n=10)
```

